---
title: "Busyness and Company's Affect on Dining Hall Attendance"
subtitle: "Mini Project 2"
author: "Lessly Ortiz, Elysia Pil, Sophia Silovsky"
format: pdf
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(Stat2Data)
library(asbio)
library(rio)
library(Stat2Data)
library(fastDummies)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
df <- import("df.csv")
df_dropped <- import("df_dropped.csv")
```

# Introduction

Humans are dependent on food, it’s a fact of life. In fact, fMRI data has found that both food and social situations both influence brain activity in the substantia nigra (Kingsland). Just as we need food, we need people. However, different variables can affect whether or not a person will get the food they need. We decided to investigate what variables affect an individual’s decision to eat, and what variables make them inclined to eat at a non-convenient dining hall. We base our hypothesis off of current research on group-based social psychology. People are more likely to conform when with friends, even if they’re in an environment they do not want to be in (Walden University). 

Our research question is: Does dining hall capacity and company affect whether or not a person goes to eat at that dining hall? Our alternative hypothesis is that as the busyness of a dining hall increases, you are less likely to stay at the dining hall if you are alone. However, you are more likely to stay if you are with friends. Our alternative hypothesis states that there will be some change in a group's likelihood to leave a dining hall based on the busyness of the dining hall and whether an individual was alone or with friends.


# Methods

For the treatment, we randomly assigned six groups of Smith students to see one of three dining hall images and one of two vignettes. The images represented the three levels of our variable "Busyness": empty, normal, busy. The images were of three Smith dining halls containing increasing amounts of people. The vignettes contained the same text, except for one line affirming the experimental, categorical "Busyness" variable and one line stating whether a person was going to a dining hall alone or with friends. The line stating whether a person was alone or with friends represents our second experimental, continuous variable "Company". To account for response variability, in the vignettes we stated that the response taker will eat at the dining hall closest to them, they are relatively hungry, and the meal is a meal they like, but not their favorite meal. 

After the survey taker saw one of the images and read one of the vignettes, they were asked how much they agree with four statements on a seven point Likert Scale from Strongly Disagree to Strongly Agree. This was our continuous dependent variable. The statements were "I would sit down and eat at this dining hall", "I would go find a new dining hall to have dinner at", "I would take the food to go", and "I would enjoy eating at this dining hall". For the sake of simplicity, this report will only go over the results of the statements, "I would sit down and eat at this dining hall". 


# Results



# Conclusion



# Resources

Kingsland, James. [Loneliness and Hunger Share a Home in the Brain](https://www.medicalnewstoday.com/articles/loneliness-and-hunger-share-a-home-in-the-brain). Medical News Today. 29 Nov. 2020.

[Why Do People Act Differently in Groups than They Do Alone](https://www.waldenu.edu/online-masters-programs/ms-in-psychology/resource/why-do-people-act-differently-in-groups-than-they-do-alone). Walden University.